---
title: "Penguin Analysis"
output: html_document
date: '2022-06-02'
---
```{r}
# set any options
```
```{r}
# load packages
library(palmerpenguins)
library(dplyr)
```



Now let's turn do doing some data analysis.  Let's use
the already cleaned penguins data set. 
Let's look at what predicts body mass of the penguins.

What would be a variable that you think would
predict body mass? 

What kind of variable is it? Is it a numeric
variable, a character or factor, or something else?

Probably there are a number of variables that you 
would be interested in.  

One powerful way to incorporate multiple variables
is using regression analysis.  So even though we
will start with just one variable, we can build
to a more complex model. 

Let's try two variables, flipper_length and sex.

How do these two variables differ?

First let's look visually.  Because the variables
are different we will use different visualizations.

```{r}
ggplot(penguins, aes(x = sex, y = body_mass_g)) +
      geom_boxplot()
```

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
      geom_point()
```

What do the relationships look like?  

Let's do something neat and combine the two in one graph.

```{r}
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
      geom_point(aes(color = sex))
```

What does this tell us? 


Now let's put this into the form of a regression model.


```{r}
lm(body_mass_g ~ sex + flipper_length_mm, data= penguins)
```

This gives us an equation for the line.  
Let's write that out.

$$ $$

```{r}
results <- lm(body_mass_g ~ sex + flipper_length_mm, data= penguins)
results
summary(results)
```

```{r}
anova(results)
```

Let's use the same process but with two different variables.
Do the plots and run the regressions.

```{r}

```

```{r}

```

What did you learn?


Now create a regression model that puts them all together.



Challenges of regression:
- assumes linearity
- significance tests have important assumptions.

